\Title

### 2021-12-27 manuscript/manuscript.tex
Update manuscript.tex

\newcommand{\Title}{Caldera-like features located over the Panikkar Seamount and adjacent regions in the Laxmi Basin, Eastern Arabian Sea}
\newcommand{\Journal}{Journal of Earth System Science}
\newcommand{\Author}{J. John Savio, V. Yatheesh, et al.}

\newcommand{\AuthorAffil}{
	{\large
		J. John Savio$^{1,2}$,
		V. Yatheesh$^{1,*}$,
		R. Sheldon$^{1}$,
		M. Kallathian$^{1}$,
		Pratima Kessarkar$^{1}$},\\
	{\large
		Kuldeep Kumar$^{1}$,
		P. Mahesh$^{1}$,
		Subhashree Mishra$^{1}$,
		and Swati Verma$^{1}$
	}
	\\[0.4cm]
	{\small $^1$ CSIR - National Institute of Oceanography, Dona Paula, Goa -  403 004, India}
	\\
	{\small $^2$ School of Earth, Ocean and Atmospheric Sciences, Goa University, Taleigao Plateau, Goa -  403 206, India}
	\\
	{\small $^*$ Corresponding author e-mail: yatheesh@nio.org}
}
\newcommand{\DOI}{\href{https://doi.org/10.xxxx/jess/xxxxxx}{https://doi.org/xxxxxx}}
\newcommand*{\doi}[1]{doi:\href{http://dx.doi.org/#1}{#1}} %% To give hyperlink to DOI's

\usepackage[left=0.7in,right=0.7in,top=0.9in,bottom=0.8in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage[round]{natbib}
\hbadness=99999
%%\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
	allcolors=blue,
	pdftitle={\Title},
	pdfauthor={\Author},
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{caption}
\fancyhf{}
\lhead{
	\fontsize{9pt}{12pt}\selectfont
	\Author{}, Accepeted article, \textit{\Journal{}}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\title{\Title}
\author{\AuthorAffil}
\date{
\normalsize
Manuscipt Received - 12 May 2021; Revised - October 2021; Accepted - 05 November 2021
\\[0.4cm] 
\justifying{
This is a pre-copyedited, author-produced version of an article accepted for publication in \textit{\Journal{}} following peer review. The version of record "\textit{John Savio, J., Yatheesh, V., Sheldon, R., Kallathian, M., Kessarkar, P., Kumar, K., Mahesh, P., Mishra, S., \&  Verma, S., 2022. \Title{}, \Journal{},}\ " is available online at: \DOI{}
}}
\maketitle

@@

	Topographic map of the northwestern continental margin of India and the adjoining deep oceans basins as depicted by the GEBCO 2021 global terrain model for ocean and land \citep{GEBCO_Compilation_Group2021}, showing the locations of the Panikkar Ridge (shown as thick white line) and the axial seamount chain in the Laxmi Basin. Thin black lines are selected (1000 m., 2000 m., 3000 m., and 4000 m.) bathymetry contours from GEBCO 2021 data set. The box shown with thick dashed black lines represents the boundary of the tectonic map shown in Figure 2. LXR: Laxmi Ridge; LXB: Laxmi Basin; ABB: Arabian Basin; PKR: Panikkar Ridge; LCP: Laccadive Plateau. R: Raman Seamount; P: Panikkar Seamount; W: Wadia Guyot

@@

		Generalized tectonic map of the northwestern continental margin of India and the adjoining deep ocean basins. The blue coloured box represents the study area. Grey coloured thin dotted lines represent the selected (200 m., 1000 m., 2000 m., 3000 m., and 4000 m.) bathymetry contours. Grey coloured continuous lines represent the inferred magnetic lineations in the Laxmi Basin  \citep{Bhattacharya2015} and the solid red coloured patches in the axial part of the Laxmi Basin represent the extent of the seamount chain \citep{Bhattacharya1994b} consisting of the Raman Seamount (R), Panikkar Seamount (P) and the Wadia Guyot (W). The green-coloured region represents the extent of the Panikkar Ridge (PKR).  Other details are as in Figure \ref{fig:studyarea}.

@@

		Colour-coded bathymetric map of the Panikkar Seamount and the adjacent regions, showing (a) the morphology of the seafloor and (b) the interpreted caldera-like features. The thin black lines represent selected (3600 m. and 3650 m.) isobaths. S1, S2 and S3 represent the Segment-1, Segment-2 and Segment-3 of the Panikkar Seamount. The labels C1 through C6 represent the locations of inferred caldera-like features. The thick black circles represent the postulated extent of rims of these inferred calderas as seen from the bathymetry data (continuous semi-circles) and as considered to have buried under the sediments (dotted semi-circles).

@@

	\captionof{figure}{ Colour-coded three-dimensional bathymetry maps representing postulated calderas (a) C1 and C2; (b) C3 and C4; and (c) C5 and C6. Other details are as in Figure \ref{panikkar}.}\label{calderas}

>>>>

\newcommand{\Title}{\textbf{Caldera-like features located over the Panikkar Seamount and adjacent regions in the Laxmi Basin, Eastern Arabian Sea}}
\newcommand{\Journal}{Journal of Earth System Science}
\newcommand{\Author}{J. John Savio, V. Yatheesh, et al.}

\newcommand{\AuthorAffil}{
	{\large
		J. John Savio$^{1,2}$,
		V. Yatheesh$^{1,*}$,
		R. Sheldon$^{1}$,
		M. Kallathian$^{1}$,
		Pratima Kessarkar$^{1}$},\\
	{\large
		Kuldeep Kumar$^{1}$,
		P. Mahesh$^{1}$,
		Subhashree Mishra$^{1}$,
		and Swati Verma$^{1}$
	}
	\\[0.4cm]
	{\small $^1$ CSIR - National Institute of Oceanography, Dona Paula, Goa -  403 004, India}
	\\
	{\small $^2$ School of Earth, Ocean and Atmospheric Sciences, Goa University, Taleigao Plateau, Goa -  403 206, India}
	\\
	{\small $^*$ Corresponding author e-mail: yatheesh@nio.org}
}
\newcommand{\DOI}{\href{https://doi.org/10.1007/s12040-021-01797-7}{10.1007/s12040-021-01797-7}}
\newcommand*{\doi}[1]{doi:\href{http://dx.doi.org/#1}{#1}} %% To give hyperlink to DOI's

\usepackage[left=0.7in,right=0.7in,top=0.9in,bottom=0.8in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage[round]{natbib}
\hbadness=99999
%%\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
	allcolors=blue,
	pdftitle={\Title},
	pdfauthor={\Author},
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{caption}
\fancyhf{}
\lhead{
	\fontsize{9pt}{12pt}\selectfont
	\Author{}, \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\title{\Title}
\author{\AuthorAffil}
\date{
\normalsize
MS received - 12 May 2021; revised - 27 October 2021; accepted - 05 November 2021
\\[0.4cm] 
\justifying{
This is a pre-copyedited, author-produced version of an article accepted for publication in \textit{\Journal{}} following peer review. The version of record "\textit{John Savio, J., Yatheesh, V., Sheldon, R., Kallathian, M., Kessarkar, P., Kumar, K., Mahesh, P., Mishra, S., \&  Verma, S., 2022. \Title{}, \Journal{},}\ " is available online at: \DOI{}
}}
\maketitle

@@

\textsl{	Topographic map of the northwestern continental margin of India and the adjoining deep oceans basins as depicted by the GEBCO 2021 global terrain model for ocean and land \citep{GEBCO_Compilation_Group2021}, showing the locations of the Panikkar Ridge (shown as thick white line) and the axial seamount chain in the Laxmi Basin. Thin black lines are selected (1000 m., 2000 m., 3000 m., and 4000 m.) bathymetry contours from GEBCO 2021 data set. The box shown with thick dashed black lines represents the boundary of the tectonic map shown in Figure \ref{fig:studyarea2}. LXR: Laxmi Ridge; LXB: Laxmi Basin; ABB: Arabian Basin; PKR: Panikkar Ridge; LCP: Laccadive Plateau. R: Raman Seamount; P: Panikkar Seamount; W: Wadia Guyot}

@@

	\textsl{	Generalized tectonic map of the northwestern continental margin of India and the adjoining deep ocean basins. The blue coloured box represents the study area. Grey coloured thin dotted lines represent the selected (200 m., 1000 m., 2000 m., 3000 m., and 4000 m.) bathymetry contours. Grey coloured continuous lines represent the inferred magnetic lineations in the Laxmi Basin  \citep{Bhattacharya2015} and the solid red coloured patches in the axial part of the Laxmi Basin represent the extent of the seamount chain \citep{Bhattacharya1994b} consisting of the Raman Seamount (R), Panikkar Seamount (P) and the Wadia Guyot (W). The green-coloured region represents the extent of the Panikkar Ridge (PKR).  Other details are as in Figure \ref{fig:studyarea}.}

@@

		\textsl{Colour-coded bathymetric map of the Panikkar Seamount and the adjacent regions, showing (a) the morphology of the seafloor and (b) the interpreted caldera-like features. The thin black lines represent selected (3600 m. and 3650 m.) isobaths. S1, S2 and S3 represent the Segment-1, Segment-2 and Segment-3 of the Panikkar Seamount. The labels C1 through C6 represent the locations of inferred caldera-like features. The thick black circles represent the postulated extent of rims of these inferred calderas as seen from the bathymetry data (continuous semi-circles) and as considered to have buried under the sediments (dotted semi-circles).}

@@

	\captionof{figure}{ \textsl{Colour-coded three-dimensional bathymetry maps representing postulated calderas (a) C1 and C2; (b) C3 and C4; and (c) C5 and C6. Other details are as in Figure \ref{panikkar}.}}
	\label{calderas}
